---
title: "Biostatistics and Data Analysis"
---

## Degree programme

- MSc / Postgraduate Diploma in Fisheries and Aquatic Resources Management, University of Sri Jayewardenepura



## About the course unit


This course is designed for students with **no prior** experience in statistics or R programming. We will start right from the basics. Each topic in this  course unit will include a practical session using R.

Why Use R Software for Data Analysis?

- Free and Open-Source

- Rapidly developing 

- Excellent for Visualization and statistical data analysis

- Active community of users and developers

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

No <- c(1, "", "", "",
        2, "",
        3, "",
        4, "",
        5, "",
        6, 
        7, "",
        8, "", "", "",
        9, "", "",
        10, "")
Topic <- c("Introdiction to Statistics", "", "", "",
           "Data Collection and Sampling", "",
           "Descriptive Statistics", "",
           "Introduction to Data Analysis with R", "",
           "Probability and Distributions", "", 
           "Statistical Inference", 
           "Parametric Tests", "",
           "Non-parametric Tests", "", "", "",
           "Correlation and Regression", "", "",
           "Way Forward", "")
Subtopic <- c("Role of statistics in zoology and biological sciences", #1
              "Types of variables: qualitative vs quantitative, continuous vs discrete, Scales of measurement",
              "Organizing Biological Data for Analysis",
              "Key Statistical Terminologies: Population, Sample, Parameter, Statistic, Descriptive statistics, Inferential statistics",
              "Random vs Non-random Sample", #2
              "Introduction to Design of Experiments",
              "Data visualisation",#3
              "Summary measures", 
              "Introduction to R and RStudio", #4
              "Exploratory Data Analysis with R",
              "Basic probability rules", #5
              "Normal distribution, binomial distribution, Poisson distribution",
              "Estimation and Hypothesis Testing ", #6
              "t-tests (one-sample, two-sample, paired)",#7
              "One-way ANOVA for comparing >2 groups",
              "Chi-square test for independence/goodness of fit", #8
              "Mann–Whitney U test", 
              "Wilcoxon signed-rank test", 
              "Kruskal–Wallis test",
              "Correlation", #9
              "Simple Linear Regression Analysis",
              "Multiple Linear Regression Analysis",
              "Getting Aware of Advanced Topics:", "Clustering, Principal Component Analysis, Spatio-temporal Data Analsysis"
              )
Materials <- rep("", length(No))
Exercises <- rep("", length(No))

df <- data.frame(No,
                 Topic,
                 Subtopic,
                 Materials,
                 Exercises)

# Create kable with highlighted rows and all others white
df %>%
  kable("html", escape = FALSE) %>%
  kable_styling(full_width = TRUE, stripe_color = NULL) %>%  # disables default striping
  row_spec(0, bold = TRUE, background = "white") %>%         # header
  row_spec(1:nrow(df), background = "white") %>%             # all rows default white
  row_spec(c(1,5,7,9,11,13,14,16,20,23), background = "#fff3cd")  # highlighted rows
```


```{r, eval=FALSE, echo=FALSE}
length(No)
length(Topic)
length(Subtopic)
length(Materials)
length(Exercises)

```