---
title: "Biostatistics and Data Analysis"
---

## Degree programme

-   MSc / Postgraduate Diploma in Fisheries and Aquatic Resources Management, University of Sri Jayewardenepura

## About the course unit

This course is designed for students with **no prior** experience in statistics or R programming. We will start right from the basics. Each topic in this course unit will include a practical session using R.

Why Use R Software for Data Analysis?

-   Free and Open-Source

-   Rapidly developing

-   Excellent for Visualization and statistical data analysis

-   Active community of users and developers

## Lecturer-in-charge

[Dr Thiyanga S. Talagala](https://thiyanga.netlify.app/)

Email: ttalagala@sjp.ac.lk

## Reference book

[Biostatistics and Data Analysis for Zoologists](https://thiyangt.github.io/BDAZ/)

## Unit Road Map

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)

# Sample data frame
df <- data.frame(
  No = c(1, "", "", "", 2, "", 3, "", 4, "", 5, "", 6, 7, "", 8, "", "", "", 9, "", "", 10, ""),
  Topic = c("Introdiction to Statistics", "", "", "", 
            "Data Collection and Sampling", "", 
            "Descriptive Statistics", "", 
            "Introduction to Data Analysis with R", "", 
            "Probability and Distributions", "", 
            "Statistical Inference", "Parametric Tests", "", 
            "Non-parametric Tests", "", "", "", 
            "Correlation and Regression", "", "", 
            "Way Forward", ""),
  Subtopic = c("Role of statistics in zoology and biological sciences",
               "Types of variables: qualitative vs quantitative, continuous vs discrete, Scales of measurement",
               "Organizing Biological Data for Analysis",
               "Key Statistical Terminologies: Population, Sample, Parameter, Statistic, Descriptive statistics, Inferential statistics",
               "Random vs Non-random Sampling",
               "Introduction to Design of Experiments",
               "Data visualisation",
               "Summary measures",
               "Introduction to R and RStudio",
               "Exploratory Data Analysis with R",
               "Basic probability rules",
               "Normal distribution, binomial distribution, Poisson distribution",
               "Estimation and Hypothesis Testing",
               "t-tests (one-sample, two-sample, paired)",
               "One-way ANOVA for comparing >2 groups",
               "Chi-square test for independence/goodness of fit",
               "Mann–Whitney U test",
               "Wilcoxon signed-rank test",
               "Kruskal–Wallis test",
               "Correlation",
               "Simple Linear Regression Analysis",
               "Multiple Linear Regression Analysis",
               "Getting Aware of Advanced Topics:",
               "Clustering, Principal Component Analysis, Spatio-temporal Data Analysis"),
  Materials = c("Slides 1"
,"Slides 2-1", "Slides 2-2", "Slides 3"
,rep("", 20)),
  Exercises = rep("", 24)
)

# Quarto HTML table without default striping
df %>%
  kable("html", escape = FALSE) %>%
  kable_styling(full_width = TRUE, bootstrap_options = "basic") %>%  # disables Quarto/Bootstrap striping
  row_spec(0, bold = TRUE, background = "white") %>%                 # header white
  row_spec(1:nrow(df), background = "white") %>%                     # all rows white
  row_spec(c(1,5,7,9,11,13,14,16,20,23), background = "#fff3cd")  
```

```{r, eval=FALSE, echo=FALSE}
length(No)
length(Topic)
length(Subtopic)
length(Materials)
length(Exercises)

```

## Slides

[Slides 1](./week1/index.html)

[Slides 2-1](./week3/index.html)

[Slides 2-2](./week4/index.html)

[Slides 3](./week2/index.html)
